Introducing the \NAME Framework\\ for Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-16 paper.tex
completed design up to semantic model

\usepackage{tikz}

@@

\begin{figure}[H]
\begin{tikzpicture}[
    nonterminal/.style={
% The shape:
rectangle,
% The size:
      minimum size=6mm,
% The border:
      very thick,
      draw=red!50!black!50,
      % The filling:
top color=white,
bottom color=red!50!black!20, % and something else at the bottom % Font
font=\itshape
    }]
  \node [nonterminal] {TODO};
\end{tikzpicture}
\caption{Overview code generation process}
\label{fig:code-generation}
\end{figure}

@@

@@

Figure \ref{fig:meta-model} shows the meta-model of the the semantic model.

\begin{figure}[H]
\begin{tikzpicture}[
    nonterminal/.style={
% The shape:
rectangle,
% The size:
      minimum size=6mm,
% The border:
      very thick,
      draw=red!50!black!50,
      % The filling:
top color=white,
bottom color=red!50!black!20, % and something else at the bottom % Font
font=\itshape
    }]
  \node [nonterminal] {TODO};
\end{tikzpicture}
\caption{Semantic Model Meta-Model}
\label{fig:meta-model}
\end{figure}

>>>>

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{graphs}
\usetikzlibrary{trees}
\usetikzlibrary{arrows}

@@

\tikzset{
  resource/.style={
    rectangle,
    minimum width=1cm,
    minimum height=8mm,
    thick, draw=black,
    top color=white,
    font=\ttfamily
  },
  representation/.style={
    rectangle, rounded corners=3mm,
    minimum width=2cm,
    minimum height=8mm,
    thick, draw=black,
    top color=white,
    font=\itshape
  }
}

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  node distance=8mm,
  ,>=stealth,thick,black!50,text=black,
  every new ->/.style={shorten >=1pt}
]
  \node (dsl)  [resource]                                 {DSL};
  \node (sm)   [representation,right=of dsl,align=center] {Semantic\\Model};
  \node (cm)   [representation,right=of sm,align=center]  {Code\\Model};
  \node (code) [resource,right=of cm]        {Code};

  \draw [->] (dsl) -> (sm)   node [midway,above=10pt]              {parse};
  \draw [->] (sm)  -> (cm)   node [midway,above=10pt,align=center] {semantic\\transform};
  \draw [->] (cm)  -> (code) node [midway,above=10pt]              {emit code};

  \draw [rounded corners,->]
        ($ (sm.east) - (5mm,4.5mm) $)
        -- ++(0,-.5)
        -| ($ (sm.west) + (5mm,-4.5mm) $)
           node [near start, below=1pt] {type inference};

  \draw [rounded corners,->]
        ($ (cm.east) - (5mm,4.5mm) $)
        -- ++(0,-.5)
        -| ($ (cm.west) + (5mm,-4.5mm) $)
           node [near start, below=1pt,align=center] {syntactic\\transform};

\end{tikzpicture}
}
\caption{Overview code generation process}
\label{fig:code-generation}
\end{figure}

The DSL is parsed and imported into a semantic model. Based on the minimal type
information present in the model, all remaining types are inferred. Through a
series of semantic transformations, the model evolves from the functional to a
more technical one, a code model. This code model can be considered as a rich
AST with an extensive set of language constructs. Syntactic transformations now
lower this level of expressiveness according to the desired platform and
language. In the end the code model can be directly emitted to the target
language.

@@

The semantic model is the core of the solution. It offers a way to describe ID
algorithms in a way that allows semantic reinterpretation. This way, the
functionality of different algorithms can be reorganised to allow for more
optimal execution and memory usage. Hence the name \NAME of the framework:
intrusion detection functionality organisation optimisation.

Figure \ref{fig:meta-model} shows the central part of the semantic model as
implemented for \NAME.

\tikzset{
  class/.style={
    rectangle,
    minimum size=1cm,
    thick, draw=black,
    text centered,
    text width=1.75cm,
  },
  subclass/.style={thick,draw=black,>=open triangle 60,<-},
  aggregate/.style={thick,draw=black,>=open diamond,<-},
  composite/.style={thick,draw=black,>=diamond,<-},
  dependency/.style={thick,>=latex,->}
}

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  edge from parent fork down,
  sibling distance=5mm, level distance=20mm, node distance=6mm
  ]
  \node (model) [class] {Model}
      child {node (module) [class] {Module} edge from parent [composite]
        child {node (strategy) [class,align=center,xshift=-9mm] {Execution\\Strategy} edge from parent [composite]
          child {node(every) [class,xshift=-9mm] {Every} edge from parent [subclass]}
          child {node (when) [class,xshift=9mm] {When} edge from parent [subclass]}
        }
        child {node (function) [class,xshift=9mm] {Function} edge from parent [composite]}
      };
  \node (constant)  [class,right=of module]   {Constant};
  \node (scope)     [class,left=of strategy]  {Scope};
  \node (statement) [class,right=of function] {Statement};
  \node (nodes)     [class,left=of module]    {Nodes\\Domain};

  \draw [aggregate]  (module)   -- (nodes);
  \draw [composite]  (module)   -- (constant);
  \draw [dependency] (strategy) -- (scope);
  \draw [composite]  (function) -- (statement);
\end{tikzpicture}
}
\caption{Partial Semantic Model for \NAME}
\label{fig:meta-model}
\end{figure}

The concept driving this model is the structure starting at the \emph{Model} up
to the \emph{Execution Strategy}. This structure surrounds the actual
\emph{Function}s and underlying \emph{Statement}s and allows for interpretation
and fusion of the algorithms.

\subsection{Function Code Fusion}

@@
